Programmer friendly communication framework

### 2024-03-08 2024_paper/paper/msglink_framework.tex
some changes

UDP stands for \textbf{User Datagram Protocol} and is . The UDP protocol finds the destination device and sends the data inform of a datagram. There is nothing set in place to ensure that the datagram reaches the destination. There is also no process set in place that tells the receiver end in which order the packets were send. A datagram has a size restriction (65.535 bytes) which the packets gets split into. \textcolor{red}{(Achtung!!!!!!!!!!!!!!!!!!!!!! wenn man mehrere geräte hat verwendet man oft eigentlich UDP da das schneller geht)}

@@

Providing solutions for these \textcolor{red}{annoyances/problems} is the job of communication frameworks or library. A communication framework does not only implement a higher level protocol to support the additional functionality, but also provides programming language functions to integrate the functionality as seamlessly as possible with language features.

@@

\begin{itemize}
    \item Abstraction of low-level socket APIs, exposing the most important functionality and automatically handle the rest in the background (according to common use-cases)
    \item Automatic management of connection state, handling disconnects and reconnects
    \item Provide a way to exchange messages, which are blocks of data of a known (but still possibly dynamic) length, guaranteeing arrival in same grouping and order as sent
    \item Provide facilities to serialize and deserialize language-native data structures to easily send them over the network (with the least code possible)
    \item Provide data validation for sent and received messages according to programmer defined schemas (in language native format as far as possible), so the user code can trust received data to be in valid format.
    \item Provide additional, commonly used communication schemes that further simplify common use cases of network communication for the developer such as Remote Procedure Calls (RPCs)
\end{itemize}

>>>>

UDP stands for \textbf{User Datagram Protocol}. Unlike TCP, UDP does not require a connection to be established. The UDP merely sends a block of data (called the user datagram) all at once to a destination host in a single IP packet. There is nothing set in place to ensure that the packet reaches the destination. Without further protocols, UDP packets do not have any relation to each other, therefore there is no insurance of the order packets are received. Since the entire datagram is sent in one IP packet, it's maximum is restricted to the limits imposed by the latter.\textcolor{red}{(65.535 bytes)} \textcolor{red}{(Achtung!!!!!!!!!!!!!!!!!!!!!! wenn man mehrere geräte hat verwendet man oft eigentlich UDP da das schneller geht)}

@@

Providing solutions for these \textcolor{red}{annoyances/problems} is the job of communication frameworks or libraries. A communication framework does not only implement a higher level protocol to support the additional functionality, but also provides programming language functions to integrate the functionality as seamlessly as possible with language features.

@@

\begin{itemize}
    \item Abstraction of low-level socket APIs, exposing the most important functionality and automatically handle the rest in the background (according to common use-cases) including but not limited to:
    \begin{itemize}
        \item Automatic management of connection state, handling disconnects and reconnects
    \end{itemize}
    \item Provide a way to exchange messages, which are blocks of data of a known (but still possibly dynamic) length, guaranteeing arrival in same grouping and order as sent
    \item Provide facilities to serialize and deserialize language-native data structures to easily send them over the network (with the least code possible)
    \item Provide data validation for sent and received messages according to programmer defined schemas (in language native format as far as possible), so the user code can trust received data to be in valid format.
    \item Provide additional, commonly used communication schemes such as Remote Procedure Calls (RPCs) that further simplify common use cases of network communication for the developer
\end{itemize}
